---
title: "Crowd4SDG Slack"
output: html_notebook
---

**** 
TODO - Map to teams 
****

Slack Analysis - Crowd4SDG

0. Load Data/Libraries

```{r, message = FALSE, warning = FALSE}

source("custom_functions.R")

library(ggplot2)
library(dplyr)
library(tidyr)

load("../processed data/slack.RData")

```


1. Networks

(i) Text mention networks - (Rathin: @Camille, blah blah.) - Directed edge from Rathin -> Camille
(ii) Emoticon Responses - Camille reacted :) to Rathin's message - Directed edge Camille -> Rathin
(iii) Bipartite user-channel

*(iii) Co-mention - (Rathin: @Camille, @Marc blah blah) - Undirected clique between Rathin, Camille and Marc

```{r}

#(i)

#Remove bulk notification (here, channel, everyone) on slack
tm_users = text_mentions[!text_mentions$cited_user %in% c("here", "channel", "everyone"),c(2,3,1,4)]

g_text_mentions = graph_from_data_frame(tm_users, vertices = users_df, directed = TRUE)
E(g_text_mentions)$weight = 1

#sample plot

pdf("../figures/slack/text_mention_network.pdf")
plt = plotNetwork(g_text_mentions)

dev.off()

```

```{r}

#(ii)

g_emoticon_responses = graph_from_data_frame(emoticons[,c(4,2,1,3,5)], vertices = users_df)
E(g_emoticon_responses)$weight = 1


pdf("../figures/slack/emoticon_responses_network.pdf")
plt = plotNetwork(g_emoticon_responses)

dev.off()


```

```{r}

#(iii)

nodes = data.frame(vertices = unique(channels_members$name), type = TRUE)
nodes = rbind(nodes, data.frame(vertices = unique(channels_members$members), type = TRUE))

g_user_channel = graph_from_data_frame(channels_members[,c(2,3,1)], vertices = nodes, directed = FALSE)

```

2. Activity

2.1 Wordclouds of Channels over time

```{r}

Sys.setenv(TZ="GMT")
texts$timestamp = as.POSIXct(as.integer(texts$timestamp), origin = "1970-01-01")

df_channel_activity_weekly = data.frame()

for (i in unique(texts$channel))
{
  obj = hist(texts$timestamp[texts$channel == i], breaks = "weeks", plot = F)
  for (j in 1:length(obj$counts))
  {
    df_channel_activity_weekly = rbind(df_channel_activity_weekly, data.frame(channel = i, activity = obj$counts[j], weeks = obj$breaks[j]))
  }
  
}
```


```{r,fig.height=5, fig.width=10}

library(wordcloud)

list = sort(unique(df_channel_activity_weekly$weeks))
weeks = list
wc = list()

pdf('../figures/slack/wordclouds_slack_week.pdf', 10, 10)

for (i in list[1:(length(list))])
{
  set.seed(1234)

  words = df_channel_activity_weekly$channel[df_channel_activity_weekly$weeks == i]
  freq = df_channel_activity_weekly$activity[df_channel_activity_weekly$weeks == i]
  
  if(max(freq) > 0)
    wc = wordcloud(words = words, freq = freq, min.freq = 0,max.words=100, random.order=FALSE, rot.per=0, colors=brewer.pal(8, "Dark2")) 
}

dev.off()

```

2.2 Activity over time - Heatmap

```{r}

library(harrypotter)

df_channel_activity_weekly$count = df_channel_activity_weekly$activity
df_channel_activity_weekly$order = 0

for (i in unique(df_channel_activity_weekly$channel))
{
  temp = df_channel_activity_weekly[df_channel_activity_weekly$channel == i,]
  df_channel_activity_weekly$count[df_channel_activity_weekly$channel == i] = (temp$count/sum(temp$count))
  
  peak = temp$week[which.max(temp$count)]
  df_channel_activity_weekly$order[df_channel_activity_weekly$channel == i] = peak
}

df_channel_activity_weekly$weeks = as.POSIXct(df_channel_activity_weekly$weeks, origin = "1970-01-01")

plt = ggplot(df_channel_activity_weekly) + geom_tile(aes(x = weeks, y = reorder(channel, -order), fill = count), lwd = 1.5, linetype = 1) + scale_fill_gradientn(colors = hp(n = 7, option = "Always")) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) + ylab("") + xlab("")

ggsave(plot = plt, filename = "../figures/slack/channel_activity_weekly.png", height = 7, width = 7)

```


Simple Bar with not normalized heatmap - same order

Activity

```{r}

a = df_channel_activity_weekly %>% group_by(channel) %>% summarise(count = sum(activity))

plt = ggplot(a, aes(y = reorder(channel, count), x = count)) + geom_bar(stat = "identity") + theme_bw(base_size = 20) + xlab("Activity") + ylab("") 

ggsave(plt, filename = "../figures/slack/channel_activity_bar.png", width = 10, height = 10)

##########################33

df_channel_activity_weekly$count = df_channel_activity_weekly$activity
df_channel_activity_weekly$order = 0

for (i in unique(df_channel_activity_weekly$channel))
{
  temp = df_channel_activity_weekly[df_channel_activity_weekly$channel == i,]
  #df_channel_activity_weekly$count[df_channel_activity_weekly$channel == i] = (temp$count/sum(temp$count))
  
  peak = temp$week[which.max(temp$count)]
  df_channel_activity_weekly$order[df_channel_activity_weekly$channel == i] = peak
}

df_channel_activity_weekly$weeks = as.POSIXct(df_channel_activity_weekly$weeks, origin = "1970-01-01")

df_channel_activity_weekly$count[df_channel_activity_weekly$count == 0] = NA
df_channel_activity_weekly = df_channel_activity_weekly %>% group_by(channel) %>% mutate(total = sum(activity))

plt = ggplot(df_channel_activity_weekly) + geom_tile(aes(x = weeks, y = reorder(channel, total), fill = count), lwd = 1.5, linetype = 1) + scale_fill_gradientn(colors = hp(n = 7, option = "Always"), na.value = "white") + theme_bw(base_size = 20) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank()) + ylab("") + xlab("") + geom_text(aes(x = weeks, y = reorder(channel, -order), label = count))

ggsave(plot = plt, filename = "../figures/slack/channel_activity_weekly_nonor.png", height = 10, width = 10)



```

Acivity Overall

```{r}

a = df_channel_activity_weekly %>% group_by(weeks) %>% summarise(count = sum(activity))

plt = ggplot(a, aes(y = count, x = weeks)) + geom_line(stat = "identity") + theme_bw(base_size = 20) + xlab("Time") + ylab("") + ggtitle("Activity over time") + geom_point(aes(x = weeks, y = count))

ggsave(plt, filename = "../figures/slack/channel_activity_time.png", width = 7, height = 7)

```


3.1 User Team mapping

```{r}
library("digest")
library(dplyr)

user_map = users_df[,c("id", "real_name", "email")]
user_map = user_map %>% rowwise() %>% mutate(email_hash = digest::digest(trimws(email), algo = "sha256", serialize = FALSE))

map = read.csv("../data/team_users_hashed.csv")

#user_map = merge(user_map, map[,c("EmailHash", "Team")], by.x = "email_hash", by.y = "EmailHash", all.x = TRUE)

user_map = read.csv("../processed data/slack_id_verified.csv", stringsAsFactors = FALSE)
user_map = user_map %>% drop_na()

```


Grouped Networks

```{r}

#Overall - mentions

text_ment = merge(text_mentions, user_map[,c("id", "Team")], by.x = "message_creator", by.y = "id")
colnames(text_ment)[colnames(text_ment) == "Team"] = "From_Team"

text_ment = merge(text_ment, user_map[,c("id", "Team")], by.x = "cited_user", by.y = "id")
colnames(text_ment)[colnames(text_ment) == "Team"] = "To_Team"

text_ment$From_Team = as.character(text_ment$From_Team)
text_ment$To_Team = as.character(text_ment$To_Team)
text_ment[is.na(text_ment)] = "dummy"

g_grouped_mentions = graph_from_data_frame(text_ment[,c("From_Team", "To_Team", "timestamp", "channel", "message_creator", "cited_user")], directed = TRUE)

E(g_grouped_mentions)$weight = 1

g_grouped_mentions = simplify(g_grouped_mentions, remove.loops = FALSE, remove.multiple = TRUE)

V(g_grouped_mentions)$print = V(g_grouped_mentions)$name

plt = visPlot(g_grouped_mentions, edgewidth = scales::rescale(E(g_grouped_mentions)$weight, to = c(1,10)), nodesize = strength(g_grouped_mentions, mode = "in"), textsize = scales::rescale(strength(g_grouped_mentions, mode = "in"), to = c(10,35)))

#write.graph(g_grouped_mentions, "networks/grouped_mentions.graphml", format = "graphml")

plt
visSave(plt, '../figures/slack/network_grouped_mention.html')

```


```{r}
#Overall - reactions

reac_ment = merge(emoticons, user_map[,c("id", "Team")], by.x = "reacted_by", by.y = "id")
colnames(reac_ment)[colnames(reac_ment) == "Team"] = "From_Team"

reac_ment = merge(reac_ment, user_map[,c("id", "Team")], by.x = "message_creator", by.y = "id")
colnames(reac_ment)[colnames(reac_ment) == "Team"] = "To_Team"

reac_ment$From_Team = as.character(reac_ment$From_Team)
reac_ment$To_Team = as.character(reac_ment$To_Team)
reac_ment[is.na(reac_ment)] = "dummy"

g_grouped_reactions = graph_from_data_frame(reac_ment[,c("From_Team", "To_Team", "timestamp", "channel", "message_creator", "reacted_by")], directed = TRUE)

E(g_grouped_reactions)$weight = 1

g_grouped_reactions = simplify(g_grouped_reactions, remove.loops = FALSE, remove.multiple = TRUE)

V(g_grouped_reactions)$print = V(g_grouped_reactions)$name

plt = visPlot(g_grouped_reactions, edgewidth = scales::rescale(E(g_grouped_reactions)$weight, to = c(1,10)), nodesize = strength(g_grouped_reactions, mode = "in"), textsize = scales::rescale(strength(g_grouped_reactions, mode = "in"), to = c(10,35)))


plt

visSave(plt, '../figures/slack/network_grouped_reactions.html')

```


Channel Level Networks

```{r}

library(RColorBrewer)

#using all interactions

net_list = list()
j = 1

df_total = text_ment[,c("message_creator", "cited_user", "From_Team", "To_Team", "channel", "timestamp")]
colnames(df_total) = c("From", "To", "From_Team", "To_Team", "channel", "timestamp")
df_total$type = "mention"

temp = reac_ment[,c("reacted_by", "message_creator", "From_Team", "To_Team", "channel", "timestamp")]
colnames(temp) =  c("From", "To", "From_Team", "To_Team", "channel", "timestamp")
temp$type = "reaction"

df_total = rbind(df_total, temp)

teams = unique(union(df_total$From_Team, df_total$To_Team))
listc = data.frame(team = teams, index = colorRampPalette(brewer.pal(8, "Set2"))(length(teams))) #Custom colour palette for different roles

user_map$Team = as.character(user_map$Team)
user_map[is.na(user_map)] = "dummy"

user_map = merge(user_map, listc, by.x = "Team", by.y = "team", all.x = TRUE) #Final merge of all defined attributes

team_channels = c("climategenderjustice", "team-water-warriors", "team-andapé-institute", "rhythm-of-bamboos", "rights-of-climate", "flood-rangers", "team-donate-water-project", "women-4-sustainable-world", "team-women-for-sustainable-world")

all_channels = unique(df_total$channel)

pdf('../figures/slack/plotNetworks_channels.pdf')
#par(mfrow=c(2,1), mar=c(0,0,2,0), cex.main=3)

#teams = unique(map$Team)

for (i in all_channels)
{
  
  subs = df_total[df_total$channel == i,]
    
  if(nrow(subs) > 0)
  {
    g_temp = graph_from_data_frame(subs, vertices = user_map[,c("id","real_name", "Team", "index")])
  
    #write.graph(g_temp, paste("channel_nets/", i, ".graphml", sep = ""), format = "graphml")
  
    E(g_temp)$weight = 1
    g_simp_temp = simplify(g_temp, remove.multiple = TRUE, remove.loops =  FALSE)
  
    g_simp_temp = delete_vertices(g_simp_temp, v = V(g_simp_temp)[degree(g_simp_temp) == 0])
    
    V(g_simp_temp)$Name = V(g_simp_temp)$Team
  
    net_list[[j]] = g_simp_temp
    
    j = j + 1
    
    plotNetwork(g_simp_temp, main = i, coms = V(g_simp_temp)$index, label = V(g_simp_temp)$Name, colors = TRUE)
  }
}

dev.off()


```

Grouped Total

```{r}

g_total = graph_from_data_frame(df_total[,c(3,4,1,2,5:7)], directed = TRUE)
E(g_total)$weight = 1
g_total_simp = simplify(g_total, remove.loops = FALSE)

plt = visPlot(g_total_simp, edgewidth = scales::rescale(E(g_total_simp)$weight, to = c(1,10)), nodesize = strength(g_total_simp, mode = "in"), textsize = scales::rescale(strength(g_total_simp, mode = "in"), to = c(10,35)))

visSave(plt, '../figures/slack/network_grouped_total.html')

```


Density order networks

```{r}


pdf('../figures/slack/plotNetworks_ordered.pdf')
par(mfrow=c(5,4), mar=c(0,0,2,0), cex.main=3)

ordered = order(sapply(net_list, edge_density))
names(net_list) = all_channels

for (i in ordered)
{
  g = net_list[[i]]
  
  plotNetwork(g, main = names(net_list)[i], coms = V(g)$index, colors = TRUE)
  
}

```

```{r}

texts = merge(texts, user_map[,c("id", "Team")], by.x = "user", by.y = "id", all.x = TRUE)

save(df_total, texts, file = "../processed data/slack_all_int.RData")

```

