---
title: "Comparing Answers"
output: html_notebook
---

Comparing Responses from Initial, evaluate and Accelerate

0. Load data

```{r}

library(dplyr)
library(plotly)
library(ggplot2)
library(wesanderson)

source("custom_functions.R")

registration = load("../processed data/registration.RData")

load("../../Evaluate/processed data/comparison_evaluate.RData",  temp_env <- new.env())
evaluate <- as.list(temp_env)

load("../processed data/comparison_accelerate.RData",  temp_env <- new.env())
accelerate = as.list(temp_env)

map = read.csv("../data/team_users_hashed.csv")
colnames(map) = c("Team", "ID", "Hash", "Mentors")

reg = merge(reg, map[,c("Team", "Hash")], by.x = "ID", by.y = "Hash")


reg_map = c("A2: Women & Technology Against Climate Change" = "T6: Women & Technology Against Climate Change", "B2: TEAM FOILED" = "T3: TEAM FOILED", "C1: Andapé Institute" = "T13: Andapé Institute", "C3: WOMER" = "T5: WOMER", "A5: Donate Water Project" = "T9: DonateWater", "B5: Rights of Climate" = "T11: Rights of Climate", "B3: Eco Winners" = "T14: Eco Winners", "B4: Women 4 Sustainable World" = "T12: Women 4 Sustainable World", "A1: Up Get App/CitiCERN" = "T7: UpGet app - CitiCERN Project", "B1: Water Warriors" = "T10: Water Warriors", "C2: PAM" = "T4: PAM", "C4: Climate Gender Justice" = "T8: Climate Gender Justice", "A3: Rhythm of Bamboos" = "T1: SDesiGn (Old name: Rhythm of Bamboos)", "C5: Ashifa Nazrin" = "C5: Ashifa Nazrin", "A4: Flood Rangers" = "T2: Flood Rangers")

reg_map = data.frame(old_name = names(reg_map), new_name = reg_map)
reg = merge(reg, reg_map, by.x = "Team", by.y = "old_name", all.x = TRUE)

```

1. Learning "Exante" questions

two questions with multiple correct answers. Counting - one point for a correct answer. 0 for wrong

(Correct Team Names)

```{r}
library(tidyr)

correct_k = c("National Statistical Offices have reservations on the use of citizen science data due to quality considerations.", "Impartiality (independence) and confidentiality are among key principles for official national data producers.")

correct_d = c("Collect data", "Analyze data","Share own data")

temp_reg = reg[,c("exante_knowledge", "exante_data", "Team", "ID")]
temp_reg = reshape2::melt(temp_reg, id = c("Team", "ID"))

temp_reg = temp_reg %>% rowwise() %>% mutate(answers = list(trimws(strsplit(value, ",")[[1]]))) %>% mutate(correct =  if (variable == "exante_knowledge") sum(answers %in% correct_k)/length(correct_k) else sum(answers %in% correct_d)/length(correct_d), hyper = if (variable == "exante_knowledge") phyper(sum(answers %in% correct_k), 2, 2, length(answers), lower.tail = FALSE) else phyper(sum(answers %in% correct_d), 3, 1, length(answers), lower.tail = FALSE))

  #mutate(correct = if ((sum(answers %in% correct_k) == length(answers) & length(answers) == 2) || (sum(answers %in% correct_d) == length(answers) & length(answers) == 3)) 1  else 0)

temp_reg$type = "registration"

temp_evaluate = as.data.frame(evaluate["ext"])
colnames(temp_evaluate) = c("ID", "Team", "exante_knowledge", "exante_data")
temp_evaluate = reshape2::melt(temp_evaluate, id = c("Team", "ID"))

temp_evaluate = temp_evaluate %>% rowwise() %>% mutate(answers = list(trimws(strsplit(value, ";")[[1]]))) %>% mutate(correct =  if (variable == "exante_knowledge") sum(answers %in% correct_k)/length(correct_k) else sum(answers %in% correct_d)/length(correct_d), hyper = if (variable == "exante_knowledge") phyper(sum(answers %in% correct_k), 2, 2, length(answers), lower.tail = FALSE) else phyper(sum(answers %in% correct_d), 3, 1, length(answers), lower.tail = FALSE))

#mutate(correct = if ((sum(answers %in% correct_k) == length(answers) & length(answers) == 2) || (sum(answers %in% correct_d) == length(answers) & length(answers) == 3)) 1  else 0)

temp_evaluate$type = "evaluate"

temp_accelerate = as.data.frame(accelerate["ext"])
colnames(temp_accelerate) = c("ID", "Team", "exante_knowledge", "exante_data")
temp_accelerate = reshape2::melt(temp_accelerate, id = c("Team", "ID"))

temp_accelerate = temp_accelerate %>% rowwise() %>% mutate(answers = list(trimws(strsplit(value, ";")[[1]]))) %>% mutate(correct =  if (variable == "exante_knowledge") sum(answers %in% correct_k)/length(correct_k) else sum(answers %in% correct_d)/length(correct_d), hyper = if (variable == "exante_knowledge") phyper(sum(answers %in% correct_k), 2, 2, length(answers), lower.tail = FALSE) else phyper(sum(answers %in% correct_d), 3, 1, length(answers), lower.tail = FALSE))
  
  #mutate(correct = if ((sum(answers %in% correct_k) == length(answers) & length(answers) == 2) || (sum(answers %in% correct_d) == length(answers) & length(answers) == 3)) 1  else 0)

temp_accelerate$type = "accelerate"

```


```{r}

df = rbind(temp_reg, temp_evaluate, temp_accelerate)
df$type = factor(df$type, levels = c("registration", "evaluate", "accelerate"))

df1 = df[,c("type", "variable", "hyper")] %>% group_by(variable, type) %>% summarise(mean = mean(hyper), se = se(hyper))

plt = ggplot(df1, aes(x = type, y = mean, color = variable, group = variable)) + geom_line() + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), width = 0) + theme_bw(base_size = 20) + ylab("HypG P-Value") + xlab("")

ggsave(plt, file = "../figures/exante_compare_hypg.png", height = 7, width = 7)

#****#

df1 = df[,c("type", "variable", "correct")] %>% group_by(variable, type) %>% summarise(mean = mean(correct), se = se(correct))

df1$variable = as.character(df1$variable)
df1$variable[df1$variable == "exante_data"] = "Data production by citizen scientists"
df1$variable[df1$variable == "exante_knowledge"] = "Knowledge on citizen science data"

plt = ggplot(df1, aes(x = type, y = mean, color = variable, group = variable)) + geom_line() + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), width = 0) + theme_bw(base_size = 20) + xlab("") + ylab("Proportion Correct Answer") + theme(legend.title = element_blank())

ggsave(plt, file = "../figures/exante_compare.png", height = 7, width = 10)



```


2. Tools and Learning about tools

```{r}
library(fmsb)

re_tools = reg[,c("ID", "Team", "tools")]
re_tools$tools = as.character(re_tools$tools)
re_tools = re_tools %>% rowwise() %>% mutate(tools = list(trimws(strsplit(tools, ",")[[1]])))
re_tools = unnest(re_tools, cols = c("tools"))
re_tools$type = "registration"

el_tools = as.data.frame(evaluate["cs_tools"])
colnames(el_tools) = c("ID", "Team", "variable", "tools")
el_tools = el_tools[] %>% rowwise() %>% mutate(tools = list(trimws(strsplit(tools, ";")[[1]]))) %>% select(-variable)
el_tools = unnest(el_tools, cols = c("tools"))
el_tools$type = "evaluate"

ac_tools = as.data.frame(accelerate["cs_tools"])
colnames(ac_tools) = c("ID", "Team", "variable", "tools")
ac_tools = ac_tools[] %>% rowwise() %>% mutate(tools = list(trimws(strsplit(tools, ";")[[1]]))) %>% select(-variable)
ac_tools = unnest(ac_tools, cols = c("tools"))
ac_tools$type = "accelerate"

```

Radar Plot - All teams

```{r}

re_tools = merge(re_tools, reg_map, by.x = "Team", by.y = "old_name", all.x = TRUE)
re_tools$Team = re_tools$new_name

re_tools = re_tools %>% select(-new_name)

tools = rbind(re_tools, el_tools, ac_tools)
tools$tools[tools$tools == "None of the above"] = "None"

temp = tools %>% group_by(tools, type) %>% summarise(count = n())
temp = temp %>% group_by(type) %>% mutate(count = count/sum(count))
temp = reshape2::acast(temp, type~tools)
temp[is.na(temp)] = 0

temp = rbind(rep(1, ncol(temp)), rep(0,ncol(temp)), temp)
temp = as.data.frame(temp)

colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )

pdf("../figures/radar_stage.pdf", paper="a4r", width=10, height=10)

radarchart( as.data.frame(temp), axistype=1 , 
    #custom polygon
    pcol=colors_border , pfcol=colors_in , plwd=4 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", cglwd=0.8,
    #custom labels
    vlcex=1.5 
    )

legend(x=1.2, y=1, legend = rownames(temp[c(5,4,3),]), bty = "n", pch=20 , col=colors_in[c(3,2,1)] , text.col = "grey", cex=1.2, pt.cex=3)

dev.off()

```
Only Teams in Accelerate

```{r}

temp = tools[tools$Team %in% unique(tools$Team[tools$type == "accelerate"]),]
temp = temp %>% group_by(tools, type) %>% summarise(count = n())

temp = temp %>% group_by(type) %>% mutate(count = count/sum(count)) 
temp = reshape2::acast(temp, type~tools)
temp[is.na(temp)] = 0

temp = rbind(rep(1, ncol(temp)), rep(0,ncol(temp)), temp)
temp = as.data.frame(temp)

colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )

pdf("../figures/radar_teams.pdf", paper="a4r", width=10, height=10)

radarchart( as.data.frame(temp), axistype=1 , 
    #custom polygon
    pcol=colors_border , pfcol=colors_in , plwd=4 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", cglwd=0.8,
    #custom labels
    vlcex=1.5 
    )

legend(x=1.2, y=1, legend = rownames(temp[c(5,4,3),]), bty = "n", pch=20 , col=colors_in[c(3,2,1)] , text.col = "grey", cex=1.2, pt.cex=3)

dev.off()

```

3.  How Often did you connect with relevant people

```{r}

el_ho = as.data.frame(evaluate["h_o"])
colnames(el_ho) = c("ID", "Team", "variable", "value", "score")
el_ho$type = "evaluate"


ac_ho = as.data.frame(accelerate["h_o"])
colnames(ac_ho) = c("ID", "Team", "variable", "value", "score")
ac_ho$type = "accelerate"


```



```{r}

ho = rbind(el_ho, ac_ho)
ho$type = factor(ho$type, levels = c("evaluate", "accelerate"))

val = sort(factor(unique(ho$value), levels = c("Never", "Less than once a week", "Once a week", "Two to three times a week", "Four times or more a week")))

ho_t = ho %>% group_by(type, variable) %>% summarise(mean = mean(score), se = se(score))

plt = ggplot(ho_t, aes(x = variable, y = mean, fill = type, color = type)) + geom_point(position = position_dodge(width = 0.3, preserve = "total")) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.3, preserve = "total"), width = 0) + theme_bw(base_size = 22) + scale_y_continuous(labels=c(0:4), breaks=0:4, limits=c(0,4)) + ylab("") + xlab("") + theme(legend.title = element_blank())

ggplotly(plt)

ggsave(plt, filename = "../figures/how_often_compare.png", width = 10, height = 5)

```

By Team1

```{r}

ho$status = "evaluate"
ho$status[ho$Team %in% unique(ho$Team[ho$type == "accelerate"])] = "accelerate"

ho$status = factor(ho$status, levels = c("evaluate", "accelerate"))

ho_t = ho %>% group_by(type, variable, status) %>% summarise(mean = mean(score), se = se(score), count = n())

plt = ggplot(ho_t[ho_t$type == "evaluate",], aes(x = variable, y = mean, fill = status, color = status)) + geom_point(position = position_dodge(width = 0.3, preserve = "total")) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.3, preserve = "total"), width = 0) + theme_bw(base_size = 22)  + ylab("") + xlab("") + ggtitle("How often did you connect with these people \n for feedback and support for your team project?") + scale_y_continuous(labels=val, breaks=0:4, limits=c(0,4))+ theme(legend.title = element_blank()) + theme(plot.title = element_text(hjust = 0.5, size = 20))

ggplotly(plt)

ggsave(plt, filename = "../figures/how_often_evaluate.png", width = 10, height = 5)

```

Communication Tools (No Slack option in evaluate - There is Other listed, but frequency is unsure)

```{r}

el_wc = as.data.frame(evaluate["w_c"])
colnames(el_wc) = c("ID", "Team", "variable", "value", "score")
el_wc$type = "evaluate"

ac_wc = as.data.frame(accelerate["w_c"])
colnames(ac_wc) = c("ID", "Team", "variable", "value", "score")
ac_wc$type = "accelerate"

wc = rbind(el_wc, ac_wc)

val = sort(factor(unique(wc$value), levels = c("Never", "Rarely", "Sometimes", "Often", "Always")))

wc_t = wc %>% group_by(type, variable) %>% summarise(mean = mean(score), se = se(score))

plt = ggplot(wc_t[!wc_t$variable == "Other...specify.in.next.question..",], aes(x = variable, y = mean, fill = type, color = type)) + geom_point(position = position_dodge(width = 0.3, preserve = "total")) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.3, preserve = "total"), width = 0) + theme_bw(base_size = 20) + scale_y_continuous(labels=val, breaks=0:4, limits=c(0,4)) + ylab("") + xlab("") + theme(axis.text.x = element_text(angle = 45))+ theme(legend.title = element_blank())

ggplotly(plt)
```

Issues (not very helpful)

```{r}

el_di = as.data.frame(evaluate["d_i"])
colnames(el_di) = c("ID", "Team", "variable", "value", "score")
el_di$type = "evaluate"

ac_di = as.data.frame(accelerate["d_i"])
colnames(ac_di) = c("ID", "Team", "variable", "value", "score")
ac_di$type = "accelerate"

di = rbind(el_di, ac_di)
di$type = factor(di$type, levels = c("evaluate", "accelerate"))

val = sort(factor(unique(di$value), levels = c("Never", "Rarely", "Sometimes", "Often", "Always")))

di_t = di %>% group_by(type, variable) %>% summarise(mean = mean(score), se = se(score))

plt = ggplot(di_t, aes(x = variable, y = mean, fill = type, color = type)) + geom_point(position = position_dodge(width = 0.3, preserve = "total")) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.3, preserve = "total"), width = 0) + theme_bw(base_size = 20)  + ylab("") + xlab("") + theme(axis.text.x = element_text(angle = 0)) + scale_y_continuous(labels=val, breaks=0:4, limits=c(0,4))+ theme(legend.title = element_blank())

ggplotly(plt)

ggsave(plt, filename = "../figures/had_issues_compare.png", width = 10, height = 7)

```

Issues (Only Accelerate Teams)

```{r}

di_t = di[di$Team %in% unique(di$Team[di$type == "accelerate"]),] %>% group_by(type, variable) %>% summarise(mean = mean(score), se = se(score))

plt = ggplot(di_t, aes(x = variable, y = mean, fill = type, color = type)) + geom_point(position = position_dodge(width = 0.3, preserve = "total")) + geom_errorbar(aes(ymin = mean-se, ymax = mean+se), position = position_dodge(width = 0.3, preserve = "total"), width = 0) + theme_bw(base_size = 20)  + ylab("") + xlab("") + theme(axis.text.x = element_text(angle = 0)) + scale_y_continuous(labels=val, breaks=0:4, limits=c(0,4))+ theme(legend.title = element_blank())

ggplotly(plt)

ggsave(plt, filename = "../figures/had_issues_compare_acc_teams.png", width = 10, height = 7)

```

Gender Analysis

```{r}

acc_team = as.character(unique(accelerate[[1]]$What.is.your.team.))

gen = reg[,c("gender", "Team")]
#gen$Teaml = reg_map[gen$Team]
gen = merge(gen, reg_map, by.x = "Team", by.y = "old_name", all.x = TRUE)
gen$Team = gen$new_name
gen = gen %>% select(-new_name)

temp = gen %>% group_by(Team, gender) %>% summarise(count = n())

temp$type = 1
temp$type[temp$Team %in% acc_team] = 2

col = wes_palette("GrandBudapest1", 3)
#col = hp(n = 3, option = "LunaLovegood")

temp$gender = factor(temp$gender, levels = c("Prefer not to say", "Male", "Female" ))

plt = ggplot(temp, aes(x = count, y = reorder(Team, type), fill = gender)) + geom_bar(stat = "identity") + theme_bw(base_size = 22) + ylab("") + xlab("") + scale_fill_manual(values = c(col[1], col[2], col[3])) + theme(legend.title = element_blank()) #+ geom_text(stat='identity', aes(label= count), hjust=-1)

ggplotly(plt)

ggsave(plt, filename = "../figures/gender_dist.png", height = 5, width = 15)

```


Background Radar

```{r}

back = reg[ ,c("new_name", "background")]

back = clean_split_mcq(back)
colnames(back) = c("Team", "bgr")

#back$background = as.character(back$background)
#back = back %>% rowwise() %>% mutate(bgr = list(trimws(strsplit(background, ",")[[1]])))

#back = unnest(back, cols = c("bgr"))

```

```{r}

temp = back[back$Team %in% acc_team,] %>% group_by(bgr, Team) %>% summarise(count = n())

temp = reshape2::acast(temp, formula = Team~bgr)
temp[is.na(temp)] = 0

temp = rbind(rep(4, ncol(temp)), rep(0,ncol(temp)), temp)
temp = as.data.frame(temp)

#colors_border=c( rgb(0.2,0.5,0.5,0.9), rgb(0.8,0.2,0.5,0.9) , rgb(0.7,0.5,0.1,0.9) )
#colors_in=c( rgb(0.2,0.5,0.5,0.4), rgb(0.8,0.2,0.5,0.4) , rgb(0.7,0.5,0.1,0.4) )

png(filename = "../figures/reg_background.png")

radarchart( as.data.frame(temp), axistype=1 , 
    #custom polygon
    plwd=4 , plty=1,
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", cglwd=0.8,
    #custom labels
    vlcex=0.5 
    )

legend(x=1.4, y=1, legend = rownames(temp[c(5,4,3),]), bty = "n", pch=20 , col=colors_in[c(3,2,1)] , text.col = "grey", cex=1.2, pt.cex=3)

dev.off()

```




Sankey Networks

```{r}

library(networkD3)
library(rbokeh)
library(webshot)

for (i in c("gender", "country_orig", "country_resid", "education", "communication", "exante_project_SDG", "background", "occupation"))
{
  
  temp = reg[ ,c("new_name", i)]
  
  temp = clean_split_mcq(temp)
  colnames(temp) = c("Team", "var")
  
  nodes = data.frame(Name = union(unique(temp$Team), unique(temp$var)))

  links = temp %>% group_by(Team, var) %>% summarise(count = n())
  links$IDsource <- match(links$Team, nodes$Name)-1 
  links$IDtarget <- match(links$var, nodes$Name)-1

  plt = sankeyNetwork(Links = links, Nodes = nodes,
                     Source = "IDsource", Target = "IDtarget",
                     Value = "count", NodeID = "Name", 
                     sinksRight=FALSE, fontSize = 15)
  #plt
  
  visSave(plt, paste("../figures/sankey/", i, "_reg.html", sep = ""))
  #widget2png(plt, paste("../figures/sankey/", i, "_reg.png", sep = ""))
  
  webshot(paste("../figures/sankey/", i, "_reg.html", sep = ""), paste("../figures/sankey/", i, "_reg.png", sep = ""))
}

```

Age by Gender

```{r}

reg$age = floor(as.numeric(difftime(as.Date("2022-04-01"), as.Date(reg$birthday, tryFormats = c("%m/%d/%Y")), unit="weeks"))/52.25)

plt = ggplot(reg, aes(x = gender, y = age)) + geom_boxplot(fill = "gray") + theme_bw(base_size = 20) + xlab("") + ylab("Age") + geom_point(aes(x = gender, y = age), alpha = 0.2)
ggplotly(plt)

ggsave(plt, filename = "../figures/age_gender.png", height = 7, width = 5)
```

